Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre

### 2024-10-18 manuscript/manuscript.Rmd
Updating README with low-res figures and relative file paths

library(egg)
nolegend_plot <- ggarrange(nmds_sla_gp+theme(legend.position = "none"), 
                           med_metab_sla_gp, ncol = 1, heights = c(0.7, 0.3), 
                           draw = FALSE)
library(cowplot)
nmds_and_med_metab <- plot_grid(nolegend_plot, get_legend(nmds_sla_gp), 
                                nrow=1, rel_widths = c(0.9, 0.1))
ggsave("fig_2_nmds_and_med_metab.tif", plot = nmds_and_med_metab, device = "tiff", 
       path = "figures", width = 6.875, height = 4.5, units = "in", dpi = 300,
       bg="white")
```

@@

# targ_gp_w_sla_frac <- egg::ggarrange(barplot_targ_gp, pc_frac_metab_gp, draw = FALSE)
# ggsave("targ_gp_w_sla_frac.png", plot = targ_gp_w_sla_frac, device = "png", 
#        path = "figures", width = 6.875, height = 4.5, units = "in", dpi = 300, 
#        bg = "white")
targ_gp_w_sla_frac <- egg::ggarrange(barplot_targ_gp, pcbarplot, pc_frac_metab_gp,
                                     draw = FALSE, heights = c(0.4, 0.2, 0.4))
ggsave("fig_3_targ_gp_w_sla_frac.tif", plot = targ_gp_w_sla_frac, device = "tif",
       path = "figures", width = 6.875, height = 5.5, units = "in", dpi = 300,
       bg = "white")
```

@@

ggsave("fig_4_MC_nmds_gp.tif", plot = MC_nmds_gp, device = "tif", 
       path = "figures", width = 6.875, height = 4.5, units = "in", dpi = 300)
```

@@

```{r kclust volcano plot combine}
kclust_volcano_gp <- egg::ggarrange(
  kclust_gp, volcanoplot_gp, 
  ncol=1, heights = c(1.5, 2), draw = FALSE)
ggsave("fig_5_kclust_volcano_gp.tif", plot = kclust_volcano_gp, device = "tif", 
       path = "figures", width = 6.875, height = 5, units = "in", dpi = 300,
       bg="white")
```

@@

ggsave("fig_6_fk_nmdsplot.tif", plot = fk_nmdsplot, device = "tif",
       path = "figures", width = 6.875, height = 4, units = "in", dpi = 300,
       bg="white")
```

>>>>

library(egg)
nolegend_plot <- ggarrange(nmds_sla_gp+theme(legend.position = "none"), 
                           med_metab_sla_gp, ncol = 1, heights = c(0.7, 0.3), 
                           draw = FALSE)
library(cowplot)
nmds_and_med_metab <- plot_grid(nolegend_plot, get_legend(nmds_sla_gp), 
                                nrow=1, rel_widths = c(0.9, 0.1))
ggsave("fig_2_nmds_and_med_metab.tif", plot = nmds_and_med_metab, device = "tiff", 
       path = "figures", width = 6.875, height = 4.5, units = "in", dpi = 300,
       bg="white")
ggsave("fig_2_nmds_and_med_metab.tif", plot = nmds_and_med_metab, device = "tiff", 
       path = "figures/lowres", width = 6.875, height = 4.5, units = "in", dpi = 72,
       bg="white")
```

@@

# targ_gp_w_sla_frac <- egg::ggarrange(barplot_targ_gp, pc_frac_metab_gp, draw = FALSE)
# ggsave("targ_gp_w_sla_frac.png", plot = targ_gp_w_sla_frac, device = "png", 
#        path = "figures", width = 6.875, height = 4.5, units = "in", dpi = 300, 
#        bg = "white")
targ_gp_w_sla_frac <- egg::ggarrange(barplot_targ_gp, pcbarplot, pc_frac_metab_gp,
                                     draw = FALSE, heights = c(0.4, 0.2, 0.4))
ggsave("fig_3_targ_gp_w_sla_frac.tif", plot = targ_gp_w_sla_frac, device = "tif",
       path = "figures", width = 6.875, height = 5.5, units = "in", dpi = 300,
       bg = "white")
ggsave("fig_3_targ_gp_w_sla_frac.tif", plot = targ_gp_w_sla_frac, device = "tif",
       path = "figures/lowres", width = 6.875, height = 5.5, units = "in", dpi = 72,
       bg = "white")
```

@@

ggsave("fig_4_MC_nmds_gp.tif", plot = MC_nmds_gp, device = "tif", 
       path = "figures", width = 6.875, height = 4.5, units = "in", dpi = 300)
ggsave("fig_4_MC_nmds_gp.tif", plot = MC_nmds_gp, device = "tif", 
       path = "figures/lowres", width = 6.875, height = 4.5, units = "in", dpi = 72)
```

@@

```{r kclust volcano plot combine}
kclust_volcano_gp <- egg::ggarrange(
  kclust_gp, volcanoplot_gp, 
  ncol=1, heights = c(1.5, 2), draw = FALSE)
ggsave("fig_5_kclust_volcano_gp.tif", plot = kclust_volcano_gp, device = "tif", 
       path = "figures", width = 6.875, height = 5, units = "in", dpi = 300,
       bg="white")
ggsave("fig_5_kclust_volcano_gp.tif", plot = kclust_volcano_gp, device = "tif", 
       path = "figures/lowres", width = 6.875, height = 5, units = "in", dpi = 72,
       bg="white")
```

@@

ggsave("fig_6_fk_nmdsplot.tif", plot = fk_nmdsplot, device = "tif",
       path = "figures", width = 6.875, height = 4, units = "in", dpi = 300,
       bg="white")
ggsave("fig_6_fk_nmdsplot.tif", plot = fk_nmdsplot, device = "tif",
       path = "figures/lowres", width = 6.875, height = 4, units = "in", dpi = 72,
       bg="white")
```
